Estimating the dynamics of SPARQL query results\thanks{This work was supported by CONICYT PFCHA, Doctorado Becas Chile/2017 -- 72180000, the Millennium Institute for Foundational Research on Data (IMFD) and FONDECYT Grant No. 1181896.}

### 2019-04-11 kgswc19.tex
Tabla y graficas terminadas

\begin{table*}[t]
	\begin{tabular}{lrrrrrrr}    \toprule
		\textbf{Classifier}        & \textsc{Q}         & \textsc{P}         & \textsc{R}         & \textsc{QP}        & \textsc{QR}        & \textsc{PR}        & \textsc{QPR}       \\    \midrule
		\textit{Random Baseline}   & 0.490  & 0.486 & 0.500   & 0.502 & 0.486 & 0.495 & 0.491 \\
		Decision Trees    & 0.471 & 0.513 & \underline{0.782} & 0.497 & 0.572 & 0.705 & 0.605 \\
		Naive Bayes       & 0.514 & \underline{0.523} & 0.764 & 0.514 & 0.540 & 0.763 & 0.540  \\
		Nearest Neighbors & 0.505 & 0.521 & 0.778 & 0.509 & 0.679 & \underline{0.781} & 0.680  \\
		Linear SVM        & \underline{0.596} & 0.518 & 0.764 & \underline{0.593} & \underline{0.775} & 0.767 & \underline{0.774} \\    \midrule
		\textbf{Better}   & 0.596 & 0.523 & 0.782 & 0.593 & 0.775 & 0.781 & 0.774 \\    \bottomrule
		\textit{Random Baseline}   & 0.487 & 0.497 & 0.500 & 0.512 & 0.502 & 0.515 & 0.501 \\
		Decision Trees    & 0.482 & 0.515 & 0.782 & 0.494 & 0.580  & 0.714 & 0.606 \\
		Naive Bayes       & 0.514 & 0.514 & 0.782 & 0.513 & 0.561 & \underline{0.797} & 0.554 \\
		Nearest Neighbors & 0.509 & \underline{0.535} & \underline{0.797} & 0.525 & 0.676 & 0.791 & 0.674 \\
		Linear SVM        & \underline{0.600} & 0.516 & 0.785 & \underline{0.590} & \underline{0.788} & 0.790  & \underline{0.788} \\    \midrule
		\textbf{Better}   & 0.600 & 0.535 & 0.797 & 0.590 & 0.788 & 0.797 & 0.788 \\    \bottomrule
		\textit{Random Baseline}   & 0.507 & 0.498 & 0.487 & 0.506 & 0.486 & 0.497 & 0.495 \\
		Decision Trees    & 0.469 & 0.514 & 0.794 & 0.457 & 0.656 & 0.731 & 0.642 \\
		Naive Bayes       & 0.517 & 0.519 & \underline{0.797} & 0.516 & 0.577 & 0.791 & 0.576 \\
		Nearest Neighbors & 0.514 & \underline{0.529} & 0.787 & 0.518 & 0.654 & \underline{0.800} & 0.65  \\
		Linear SVM        & \underline{0.578} & 0.512 & \underline{0.797} & \underline{0.571} & \underline{0.796} & \underline{0.800} & \underline{0.796} \\    \midrule
		\textbf{Better}   & 0.578 & 0.529 & 0.797 & 0.571 & 0.796 & 0.800 & 0.796 \\    \bottomrule
		\textit{Random Baseline}   & 0.514 & 0.515 & 0.502 & 0.493 & 0.499 & 0.499 & 0.502 \\
		Decision Trees    & 0.512 & 0.517 & \underline{0.827} & 0.493 & 0.725 & 0.716 & 0.704 \\
		Naive Bayes       & 0.515 & \underline{0.519} & \underline{0.827} & 0.508 & 0.599 & 0.810  & 0.594 \\
		Nearest Neighbors & 0.549 & 0.481 & \underline{0.827} & 0.555 & 0.744 & 0.821 & 0.732 \\
		Linear SVM        & \underline{0.554} & \underline{0.519} & \underline{0.827} & \underline{0.560} & \underline{0.819} & \underline{0.831} & \underline{0.815} \\    \midrule
		\textbf{Better}   & 0.554 & 0.519 & 0.827 & 0.560 & 0.819 & 0.831 & 0.815 \\    \bottomrule
	\end{tabular}
\end{table*}

@@

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.596)(2,0.600)(3,0.578)(4,0.554)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.523)(2,0.535)(3,0.529)(4,0.519)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.782)(2,0.797)(3,0.797)(4,0.827)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.593)(2,0.590)(3,0.571)(4,0.560)
	};

		\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.775)(2,0.788)(3,0.796)(4,0.819)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.781)(2,0.797)(3,0.800)(4,0.831)
	};

@@

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.49)(2,0.600)(3,0.578)(4,0.554)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.486)(2,0.535)(3,0.529)(4,0.519)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.5)(2,0.797)(3,0.797)(4,0.827)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.502)(2,0.590)(3,0.571)(4,0.560)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.486)(2,0.788)(3,0.796)(4,0.819)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.495)(2,0.797)(3,0.800)(4,0.831)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.491)(2,0.788)(3,0.796)(4,0.815)
	};

@@

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.596)(2,0.600)(3,0.578)(4,0.554)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.523)(2,0.535)(3,0.529)(4,0.519)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.782)(2,0.797)(3,0.797)(4,0.827)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.593)(2,0.590)(3,0.571)(4,0.560)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.775)(2,0.788)(3,0.796)(4,0.819)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.781)(2,0.797)(3,0.800)(4,0.831)
	};

>>>>

% Please add the following required packages to your document preamble:
% \usepackage[normalem]{ulem}
% \useunder{\uline}{\ul}{}
\begin{table*}[t]
	\begin{tabular}{lrrrrrrr}    \toprule
		\textbf{Classifier}        & \textsc{Q}         & \textsc{P}         & \textsc{R}         & \textsc{QP}        & \textsc{QR}        & \textsc{PR}        & \textsc{QPR}       \\    \midrule
		\textit{Random Baseline} & 0.499          & 0.489          & 0.502          & 0.489          & 0.495          & 0.495          & 0.516          \\
		Decision Trees           & 0.497          & \underline{0.519}    & \underline{0.781}    & 0.497          & 0.569          & 0.706          & 0.6            \\
		Naive Bayes              & 0.432          & 0.419          & 0.758          & 0.432          & 0.478          & 0.759          & 0.479          \\
		Nearest Neighbors        & 0.505          & 0.517          & 0.776          & 0.509          & 0.679          & \underline{0.781}    & 0.68           \\
		Linear SVM               & \underline{0.596}    & 0.372          & 0.758          & \underline{0.593}    & \underline{0.775}    & 0.762          & \underline{0.774}    \\    \midrule
		\textbf{Better}          & \textbf{0.596} & \textbf{0.519} & \textbf{0.781} & \textbf{0.593} & \textbf{0.775} & \textbf{0.781} & \textbf{0.774} \\    \bottomrule
		\textit{Random Baseline} & 0.48           & 0.496          & 0.499          & 0.505          & 0.495          & 0.497          & 0.499          \\
		Decision Trees           & 0.485          & 0.514          & 0.782          & 0.494          & 0.581          & 0.711          & 0.603          \\
		Naive Bayes              & 0.431          & 0.486          & 0.782          & 0.432          & 0.508          & \underline{0.797}    & 0.5            \\
		Nearest Neighbors        & 0.517          & \underline{0.535}    & \underline{0.795}    & 0.525          & 0.676          & 0.79           & 0.673          \\
		Linear SVM               & \underline{0.6}      & 0.384          & 0.784          & \underline{0.59}     & \underline{0.787}    & 0.789          & \underline{0.787}    \\    \midrule
		\textbf{Better}          & \textbf{0.6}   & \textbf{0.535} & \textbf{0.795} & \textbf{0.59}  & \textbf{0.787} & \textbf{0.797} & \textbf{0.787} \\    \bottomrule
		\textit{Random Baseline} & 0.497          & 0.505          & 0.493          & 0.483          & 0.497          & 0.511          & 0.515          \\
		Decision Trees           & 0.456          & 0.517          & 0.793          & 0.48           & 0.668          & 0.735          & 0.651          \\
		Naive Bayes              & 0.434          & 0.461          & \underline{0.797}    & 0.435          & 0.531          & 0.79           & 0.531          \\
		Nearest Neighbors        & 0.514          & \underline{0.528}    & 0.787          & 0.517          & 0.653          & \underline{0.8}      & 0.648          \\
		Linear SVM               & \underline{0.578}    & 0.397          & \underline{0.797}    & \underline{0.571}    & \underline{0.795}    & \underline{0.8}      & \underline{0.796}    \\    \midrule
		\textbf{Better}          & \textbf{0.578} & \textbf{0.528} & \textbf{0.797} & \textbf{0.571} & \textbf{0.795} & \textbf{0.8}   & \textbf{0.796} \\    \bottomrule
		\textit{Random Baseline} & 0.486          & 0.494          & 0.482          & 0.512          & 0.524          & 0.511          & 0.49           \\
		Decision Trees           & 0.511          & \underline{0.511}    & \underline{0.827}    & 0.469          & 0.712          & 0.712          & 0.71           \\
		Naive Bayes              & 0.416          & 0.465          & 0.826          & 0.414          & 0.555          & 0.81           & 0.554          \\
		Nearest Neighbors        & 0.548          & 0.48           & 0.826          & 0.554          & 0.744          & 0.82           & 0.731          \\
		Linear SVM               & \underline{0.554}    & 0.438          & 0.826          & \underline{0.56}     & \underline{0.819}    & \underline{0.831}    & \underline{0.815}    \\    \midrule
		\textbf{Better}          & \textbf{0.554} & \textbf{0.511} & \textbf{0.827} & \textbf{0.56}  & \textbf{0.819} & \textbf{0.831} & \textbf{0.815}	\\    \bottomrule
	\end{tabular}
\end{table*}

@@

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.596)(2,0.6)(3,0.578)(4,0.554)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.519)(2,0.535)(3,0.528)(4,0.511)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.781)(2,0.795)(3,0.797)(4,0.827)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.593)(2,0.59)(3,0.571)(4,0.56)
	};

		\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.775)(2,0.787)(3,0.795)(4,0.819)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.781)(2,0.797)(3,0.8)(4,0.831)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.774)(2,0.787)(3,0.796)(4,0.815)
	};

@@

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.598)(2,0.601)(3,0.601)(4,0.619)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.52)(2,0.535)(3,0.528)(4,0.512)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.796)(2,0.798)(3,0.798)(4,0.828)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.596)(2,0.591)(3,0.589)(4,0.579)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.775)(2,0.787)(3,0.795)(4,0.819)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.782)(2,0.797)(3,0.8)(4,0.831)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.774)(2,0.787)(3,0.796)(4,0.815)
	};

@@

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.598)(2,0.601)(3,0.579)(4,0.554)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.52)(2,0.535)(3,0.528)(4,0.512)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.787)(2,0.794)(3,0.798)(4,0.828)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.595)(2,0.591)(3,0.572)(4,0.561)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.775)(2,0.787)(3,0.796)(4,0.819)
	};

	\addplot[
	color=blue,
	mark=diamond,
	]
	coordinates {
		(1,0.783)(2,0.797)(3,0.8)(4,0.831)
	};
